Multi-line Intensity Mapping

### 2019-07-10 paper/ms.tex
Add covariance matrix to multifield section
Remove shot noise

The intrinsic emission from a line $i$ is given by
\beq\label{eq:int_ps}
P_{i,i}(k, \mu, z) = \avg{I_i}^2 \avg{b_i}^2 (1 + \beta_i \mu^2)^2 
              D\left[\mu k \sigma_p(z)\right] P_{\delta, \delta}(k, z)
              + P_{i, \text{shot}}\text{,}
\eeq
where $\mu=k_{\parallel}/k$ is the cosine of the angle between the wavevector
$\bm{k}$ and the line of sight direction, $\avg{I_i}$ is the average specific
intensity of line $i$, and $\avg{b_i}$ is the average luminosity-weighted bias
of the emitting galaxies. The Kaiser effect {\bf Kaiser 1987} is implemented
through the $(1 + \beta_i \mu^2)^2$ factor, where $\beta_i =
f_{\Omega}/\avg{b_i}$ with $f_{\Omega} = \text{d}\ln{D}/\text{d}\ln{a}$ is the
logarithmic derivative of the growth factor, well approximated by $f_{\Omega}
\approx \Omega^{0.55}$ {\bf Linder 2005}. We assume a Lorentzian form for the
finger-of-god suppression:
\beq\label{eq:fog}
D(x) = \frac{1}{1+x^2}\text{.}
\eeq
We approximate the pairwise velocity dispersion by $\sigma_p(z) =
\sigma_v(z)/\sqrt{2}$ with $\sigma_v^2(z)$ being the variance of the
line-of-sight component of the velocity field according to linear theory. We
use the {\bf Eisenstein and Hu 1998} model for the linear theory matter power
spectrum, $P_{\delta,\delta}(k, z)$. The computation of the shot noise,
$P_{i,\text{shot}}$ is given in Appendix~\ref{app:co_int}. All basic
cosmological calculations are performed using the code \texttt{colossus} {\bf
Diemer 2018}.

For the cross-spectrum between two lines $i$ and $j$, we assume that {\bf need
to fix this with the shot noise component}
\beq\label{eq:cross_spec}
P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}
\eeq

\subsection{Multi-line Formalism}\label{ssec:multi_line}
Given a set of cross-spectra and their covariance matrix, we can determine the
optimal constraints that can be placed on both the average bias $\avg{b_i}$
and average intensity $\avg{I_i}$. For the set of parameters $\theta$
containing each $\avg{b_i}$ and $\avg{I_i}$, we can write down the Fisher
matrix as
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{l} \sum_{m}
\frac{\partial \hat{P}_{l}(\bm{k})}{\partial \theta_i}
\left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
\frac{\partial \hat{P}_{m}(\bm{k})}{\partial \theta_j}\text{,}
\eeq
where the sum over $l$ and $m$ each is over each \emph{pair} of lines.

@@

Eventually it will be desirable to place constraints on $\denps(k)$. For now,
however, we simply wish to understand how well future experiments will be able
to determine each of $B_i$ as a function of $z$. We can proceed simply by
computing the relevant Fisher matrix:
\beq\label{eq:fisher_tf}
F_{i,j} = 
\int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{l} \sum_{m}
\frac{\partial \hat{P}_{l}(\bm{k})}{\partial B_i}
\left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
\frac{\partial \hat{P}_{m}(\bm{k})}{\partial B_j}\text{,}
\eeq
where the sum over $l$ and $m$ each is over every \emph{pair} of lines.
Equation~\ref{eq:fisher_tf} can be readily modified to accomodate the case of
more than three lines (by extending the summations to include these lines) and
to accomodate the auto-spectra (by extending the sum over $l$ and $m$ to
include them). We will consider these cases in Sections~\Gus{x}~and~\Gus{y},
respectively.

>>>>

The intrinsic emission from a line $i$ is given by
\beq\label{eq:int_ps}
P_{i,i}(k, \mu, z) = \avg{I_i}^2 \avg{b_i}^2 (1 + \beta_i \mu^2)^2 
              D\left[\mu k \sigma_p(z)\right] P_{\delta, \delta}(k, z)\text{,}
              % + P_{i, \text{shot}}\text{,}
\eeq
where $\mu=k_{\parallel}/k$ is the cosine of the angle between the wavevector
$\bm{k}$ and the line of sight direction, $\avg{I_i}$ is the average specific
intensity of line $i$, and $\avg{b_i}$ is the average luminosity-weighted bias
of the emitting galaxies. The Kaiser effect {\bf Kaiser 1987} is implemented
through the $(1 + \beta_i \mu^2)^2$ factor, where $\beta_i =
f_{\Omega}/\avg{b_i}$ with $f_{\Omega} = \text{d}\ln{D}/\text{d}\ln{a}$ is the
logarithmic derivative of the growth factor, well approximated by $f_{\Omega}
\approx \Omega^{0.55}$ {\bf Linder 2005}. We assume a Lorentzian form for the
finger-of-god suppression:
\beq\label{eq:fog}
D(x) = \frac{1}{1+x^2}\text{.}
\eeq
We approximate the pairwise velocity dispersion by $\sigma_p(z) =
\sigma_v(z)/\sqrt{2}$ with $\sigma_v^2(z)$ being the variance of the
line-of-sight component of the velocity field according to linear theory.
Equation~\eqref{eq:int_ps} neglects the shot noise component of the power
spectrum, which is an acceptable omission for the large scales considered in
this work. We use the {\bf Eisenstein and Hu 1998} model for the linear theory
matter power spectrum, $P_{\delta,\delta}(k, z)$. All basic cosmological
calculations are performed using the code \texttt{colossus} {\bf Diemer 2018}.

For the cross-spectrum between two lines $i$ and $j$, we assume that
\beq\label{eq:cross_spec}
P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}
\eeq

\subsection{Multi-line Formalism}\label{ssec:multi_line}
Given a set of cross-spectra and their covariance matrix, we can determine the
optimal constraints that can be placed on both the average bias $\avg{b_i}$
and average intensity $\avg{I_i}$. For the set of parameters $\theta$
containing each $\avg{b_i}$ and $\avg{I_i}$, we can write down the Fisher
matrix as
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{l} \sum_{m}
\frac{\partial \hat{P}_{l}(\bm{k})}{\partial \theta_i}
\left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
\frac{\partial \hat{P}_{m}(\bm{k})}{\partial \theta_j}\text{,}
\eeq
where the sum over $l$ and $m$ each is over each \emph{pair} of lines. In
order to compute the covariance matrix, we use the result that (cite {\bf
something? Visbal?})
\beq\label{eq:var_cov}
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{,}
\end{split}
\eeq
where $\pstot{i} = \ps{i} + N_i$. Note that $N_i$ contains contributions from
instrument noise, residual foreground contamination, and
interloping/extraloping lines.

@@

Eventually it will be desirable to place constraints on $\denps(k)$. For now,
however, we simply wish to understand how well future experiments will be able
to determine each of $B_i$ as a function of $z$. We can proceed simply by
computing the relevant Fisher matrix:
\beq\label{eq:fisher_tf}
F_{i,j} = 
\int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
\sum_{l} \sum_{m}
\frac{\partial \hat{P}_{l}(\bm{k})}{\partial B_i}
\left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
\frac{\partial \hat{P}_{m}(\bm{k})}{\partial B_j}\text{,}
\eeq
where the sum over $l$ and $m$ each is over every \emph{pair} of lines.
Equation~\ref{eq:fisher_tf} can be readily modified to accomodate the case of
more than three lines (by extending the summations to include these lines) and
to accomodate the auto-spectra (by extending the sum over $l$ and $m$ to
include them). We will consider these cases in Sections~\Gus{x}~and~\Gus{y},
respectively.
